---
title: "Problem Set 4"
author: "Rebecca Xi"
date: "3/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidycensus)

#

income <- get_acs(
  geography = "county",
  variables = "B19013_001",
  cache_table = FALSE,
  year = 2018
)
```

## Question #1: Mad Libs

```{r Mad Libs 1, include=FALSE}

# This function should take a numeric vector (like our column, estimate) and
# calculate the standard deviation of the variable, then adds 1.

# To get the code to run, I added the missing parentheses at the end of return(x
# to make it return(x). As per the Piazza post, I also moved the +1 from inside
# the sd() to outside, since the function is supposed to calculate standard
# deviation first and then add 1. After seeing my answer come out in scientific
# notation in my knitted html, I used options("scipen") to get rid of that
# formatting in my final answer.

options("scipen" = 999)

sd_plus_one <- function(var, na.rm = TRUE){
  x<- sd(var, na.rm = na.rm) + 1
  return(x)
  }

r1 <- sd_plus_one(var = income$estimate)
```

ML 1) (Note that for all the madlibs you must call the function to receive points for this question: you cannot just manually calculate the mad lib result.) The standard deviation of median income, plus one, is `r r1`.


```{r Mad Libs 2, include=FALSE}

# This function should take a county and state pair and extracts just the state
# name. We can do this easily because the state name is always after a comma and
# space.

# To get the code to run, I added in the missing pipe operator from countystate
# to str_split_fixed

 get_state <- function(countystate){
  countystate %>% 
  str_split_fixed(.,", ", 2) %>% 
  pluck(2) %>% 
  return()
 }

r2 <- get_state("Treasure County, Montana")
```

ML 2) Treasure County, Montana is located in the state of `r r2`.


```{r Mad Libs 3, include=FALSE}

# This function should take the geoid for a given county, grabs the median
# income for the corresponding county, and then add the margin of error to the
# value.

# To get the code to run, I removed the extra closing parentheses from the end
# of pull(). I also changed the argument x in function(x) to geoid, for
# function(geoid), since geoid is the name of the argument we enter later. I
# also fixed the discrepancy between r code chunk and Mad Lib prompt by changing
# the given geoid from "01005" to "01055". As before, I used options("scipen")
# to get rid of the strange scientific notation formatting in my final answer.

options("scipen" = 999)

upper_bound <- function(geoid){
 income %>% 
 filter(GEOID == geoid) %>% 
 mutate(estimate + moe) %>% 
 pull()
}

r3 <- upper_bound(geoid = "01055")
```

ML 3) The upper bound for median income in Etowah County, Alabama (geoid = 
“01055”) is `r r3`.


## Question #2: Mapping










